---
title: "mapping"
author: "Alex McClymont"
date: "March 22, 2018"
output: html_document
---

#1. Using csv of sample locations
```{r}
library(ggplot2)
library(rgdal)
library(maps)
library(mapproj)
library(ggmap)
library(dplyr)
library(rgeos)

setwd("C:/Users/Alex/Desktop/Bio812/Group assignment")
samples.dat <- read.csv("./Data/Excel/SampleLocations.csv")
samples <- samples.dat %>% rename(Site = ï..Site)


#Extracting just the coordinates
#But in reality I want them to keep their labels

#only need this part if you're going to make maps in R
lat <- samples[ ,2]
long <- samples[ ,3]
coord <- as.data.frame(cbind(lat, long))
CentralPoint <- c(long[1], lat[1])

```


#Background sat map of the area
```{r}
#Centered around point 5
pt5 <- c(long[5], lat[5])
pt5_map <- ggmap(get_map(pt5, source="google", maptype = "satellite", zoom=7)) + geom_point(aes(x=long, y=lat), colour = "red", data=coord)
pt5_map

#what else do we want on a map?

#50km buffer, wind direction, industry sites?
```


##Making buffer and point shapefiles in UTM
```{r}
coordinates(samples) <- c( "Long", "Lat")
proj4string(samples) <- CRS("+proj=longlat +datum=NAD83" )
ProjectedSamples <- spTransform(samples, CRS("+init=epsg:3403" )) #assigning projection 
#now it's a spatial data frame, != a data frame


#to buffer, data needs to be in UTM
SamplesUTM <- spTransform(samples, CRS("+proj=utm +zone=12 ellps=NAD83"))

#Try from here with new projection

#write sample locations to shapefile
writeOGR(SamplesUTM, "SampleLocations", "SampleLocations", driver="ESRI Shapefile" ) 

#buffer around central point from UTM converted points
buff50cent <- gBuffer(SamplesUTM[1,], width=50000, byid=TRUE ) 
# Add data, and write buffer to shapefile
writeOGR(buff50cent, "Buff50km", "Buff50km", driver="ESRI Shapefile" ) #YA BOI

#would actually be great to have a larger, rectangular buffer that I can clip all my shapefiles to if I end up 
#even using QGIS
buffArea <- gBuffer(SamplesUTM[3, ], width=200000, capStyle="SQUARE", byid=TRUE) #bigger would be better
writeOGR(buffArea, "BuffArea", "BuffArea", driver="ESRI Shapefile") #still looks weird, but less weird

#Can i add these buffers to my map in R?
```


Can I use R to clip pipelines and other data?
Pipelines and wellsites are already in NAD83, so they don't need to be converted

Clipping pipelines to large area
```{r}
pipelines <- readOGR(dsn="./Data/Shapefiles", layer="Pipelines_GCS_NAD83")
clipPipelines <- gIntersection(pipelines, buffArea, byid=TRUE)
```


#Maybe add EC PAH data to Samples so that it can be displayed on map?
#how else to disply PAH data?

#Just select rows from PAH data that are from the sample locations
site = KAR6, KST2, KMU1, P51, KAR10, S46
```{r}
EC_PAH <- read.csv("./Data/Excel/Snow-PolycyclicAromaticCompounds-2012-2014-v1.csv")

KAR6 <- subset(EC_PAH, Site.ID == "KAR-6")
KST2 <- subset(EC_PAH, Site.ID == "KST-2")
KMU1 <- subset(EC_PAH, Site.ID == "KMU-1")
P51 <- subset(EC_PAH, Site.ID == "P51") #no data from P51
KAR10 <- subset(EC_PAH, Site.ID == "KAR-10")
S46 <- subset(EC_PAH, Site.ID == "S-46") #no data from S46 - do these locations maybe have alternate names?

#where data exists there are multiple lines from different dates - take the average or the most recent?

#for all want sum of all PAH columns

#can't calculate sum because all my variables are factors - need to make values for all PAHs numeric, but can't convert all columns because then I'll lose the info for site location and date
EC_PAH1 <- EC_PAH %>% mutate( Naphthalene=as.numeric(Naphthalene), Acenaphthylene=as.numeric(Acenaphthylene), Acenaphthene=as.numeric(Acenaphthene), Fluorene=as.numeric(Fluorene), Phenanthrene=as.numeric(Phenanthrene), Anthracene=as.numeric(Anthracene), Fluoranthene=as.numeric(Fluoranthene), Pyrene=as.numeric(Pyrene), Benzo.a.fluorene=as.numeric(Benzo.a.fluorene), Benzo.b.fluorene=as.numeric(Benzo.b.fluorene), Benzo.g.fluoranthene=as.numeric(Benzo.g.fluoranthene), Benz.a.anthracene=as.numeric(Benz.a.anthracene), Triphenylene=as.numeric(Triphenylene), Chrysene=as.numeric(Chrysene), Benzo.b.fluoranthene=as.numeric(Benzo.b.fluoranthene), Benzo.k.fluoranthene=as.numeric(Benzo.k.fluoranthene), Benzo.e.pyrene=as.numeric(Benzo.e.pyrene), Perylene=as.numeric(Perylene), Indeno.1.23.c.d.fluoranthene=as.numeric(Indeno.1.23.c.d.fluoranthene), Indeno.1.2.3.cd.pyrene=as.numeric(Indeno.1.2.3.cd.pyrene), Dibenzo.ah.anthracene=as.numeric(Dibenzo.ah.anthracene), Benzo.b.chrysene=as.numeric(Benzo.b.chrysene), Benzo.g.perylene=as.numeric(Benzo.g.perylene), Anthanthrene=as.numeric(Anthanthrene), C1.Naphthalene=as.numeric(C1.Naphthalene), C2.Naphthalene=as.numeric(C2.Naphthalene), C3.Naphthalene=as.numeric(C3.Naphthalene), C4.Naphthalene=as.numeric(C4.Naphthalene), C1.Fluorene=as.numeric(C1.Fluorene), C2.Fluorene=as.numeric(C2.Fluorene), C3.Fluorene=as.numeric(C3.Fluorene), C4.Fluorene=as.numeric(C4.Fluorene), C1.Phenanthrene.Anthracene=as.numeric(C1.Phenanthrene.Anthracene), C2.Phenanthrene.Anthracene=as.numeric(C2.Phenanthrene.Anthracene), C3.Phenanthrene.Anthracene=as.numeric(C3.Phenanthrene.Anthracene), C4.Phenanthrene.Anthracene=as.numeric(C4.Phenanthrene.Anthracene), Retene=as.numeric(Retene), C1.Fluoranthene.Pyrene=as.numeric(C1.Fluoranthene.Pyrene), C2.Fluoranthene.Pyrene=as.numeric(C2.Fluoranthene.Pyrene), C3.Fluoranthene.Pyrene=as.numeric(C3.Fluoranthene.Pyrene), C4.Fluoranthene.Pyrene=as.numeric(C4.Fluoranthene.Pyrene), C1.BaA.TRI.CHR=as.numeric(C1.BaA.TRI.CHR), C2.BaA.TRI.CHR=as.numeric(C2.BaA.TRI.CHR), C3.BaA.TRI.CHR=as.numeric(C3.BaA.TRI.CHR), C4.BaA.TRI.CHR=as.numeric(C4.BaA.TRI.CHR), X3.Methylcholanthrene=as.numeric(X3.Methylcholanthrene), Dibenzotophene=as.numeric(Dibenzotophene), C1.Dibenzotophene=as.numeric(C1.Dibenzotophene), C2.Dibenzotophene=as.numeric(C2.Dibenzotophene), C3.Dibenzotophene=as.numeric(C3.Dibenzotophene), C4.Dibenzotophene=as.numeric(C4.Dibenzotophene), Benzo.a.pyrene = as.numeric(Benzo.a.pyrene)) 


#Add new column to EC_PAH that's the sum of all PAHs
EC_PAH1 <- EC_PAH1 %>% mutate(sum = Naphthalene + Acenaphthylene + Acenaphthene + Fluorene + Phenanthrene + Anthracene + Fluoranthene + Pyrene + Benzo.a.fluorene + Benzo.b.fluorene + Benzo.g.fluoranthene + Benz.a.anthracene + Triphenylene + Chrysene + Benzo.b.fluoranthene + Benzo.k.fluoranthene + Benzo.e.pyrene + Benzo.a.pyrene + Perylene + Indeno.1.23.c.d.fluoranthene + Indeno.1.2.3.cd.pyrene + Benzo.b.chrysene + Benzo.g.perylene + Anthanthrene + C1.Naphthalene + C2.Naphthalene + C3.Naphthalene + C4.Naphthalene + C1.Fluorene + C3.Fluorene + C2.Fluorene + C4.Fluorene + C1.Phenanthrene.Anthracene + C2.Phenanthrene.Anthracene + C3.Phenanthrene.Anthracene + C4.Phenanthrene.Anthracene + Retene + C1.Fluoranthene.Pyrene + C2.Fluoranthene.Pyrene + C3.Fluoranthene.Pyrene + C4.Fluoranthene.Pyrene + C1.BaA.TRI.CHR + C2.BaA.TRI.CHR + C3.BaA.TRI.CHR + C4.BaA.TRI.CHR + X3.Methylcholanthrene + Dibenzotophene + C1.Dibenzotophene + C2.Dibenzotophene + C3.Dibenzotophene + C4.Dibenzotophene)
```

#MAYBE use sum of PAHs across all sites to create raster map?

```{r}
#Could try to make raster in R

#Or could make a point shapefile of PAH sums and use that in QGIS
#If I do this, probably best to only use data from 2014

#Selecting PAH data for 2014 only
PAH_2014 <- subset(EC_PAH1, Date=="2014")

#Now only want columns SiteID, Lat, Long, sum

PAH2014_1 <- subset(PAH_2014, select = c("Latitude", "Longitude", "sum"))

#Export as raster shapefile
PAH2014_1$Latitude <- as.numeric(as.character(PAH2014_1$Latitude))
PAH2014_1$Longitude <- as.numeric(as.character(PAH2014_1$Longitude))
coordinates(PAH2014_1) <- c( "Longitude", "Latitude")
proj4string(PAH2014_1) <- CRS("+proj=longlat +datum=NAD83" )

writeOGR(PAH2014_1, "PAH2014", "PAH2014", driver="ESRI Shapefile") 

#Now want to make PAHs a raster data set within my large area buffer, based on "sum"

library(raster)

require(raster)
projection(PAH2014_1) = "+datum=NAD83 +init=espg:3403"
shapefile(PAH2014_1, "PAH2014", overwrite=T)
```




